Four decades of water quality change in the upper San Francisco Estuary

### 2017-01-09 sftrends_manu.Rnw
dynaplot to fig dinc10

% \usepackage[version=3]{mhchem}
\usepackage[T1]{fontenc}
\usepackage[colorlinks  =true, allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{lineno}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage{paralist}
\usepackage{bm}
\usepackage{fixltx2e}
% \usepackage{showlabels}

@@

The goal of this study was to provide a comprehensive description of nutrient trends in the Delta that will inform understanding of eutrophication dynamics and potential causes of water quality change in the larger Bay. We applied the newly-adapted method of weighted regression for tidal waters to describe nitrogen trends in  different spatial and temporal contexts. The specific objectives were to \begin{inparaenum}[1\upshape)]  
\item quantify and interpret trends over four decades at ten stations in the Delta, including annual, seasonal, and spatial changes in nitrogen analytes and response to flow variation,
\item provide detailed descriptions of three case studies in the context of conceptual relationships modelled with \ac{wrtds}.
\end{inparaenum}
The second objective evaluated three specific water quality stations in the Delta to demonstrate complexities with nutrient response to flow, effects of \ac{wwtp} upgrades on water quality, and effects of biological invasion by benthic filter feeders on primary production. Although quantitative descriptions of change can be ends in themselves, the results were expected to have greater impact as a means to more detailed understanding of ecosystem properties.  Products derived from \ac{wrtds} can be used to inform additional analyses, such as water quality response after removing annual, seasonal, or flow effects. Overall, this analysis is expected to further an ecological and management-based understanding of dynamics in San Francisco Bay, with implications for water quality restoration and protection of this prominent system.

@@

\subsection{Case studies}

Three stations were chosen for closer evaluation to demonstrate use of \ac{wrtds} to develop a more comprehensive description of decadal trends in the Delta.  The stations were chosen to address ecological and management-based questions that have relevance outside of the region, having importance for the understanding of estuarine processes that influence eutrophication trends over several years.  The selected case studies focused on \begin{inparaenum}[1\upshape)]
\item nitrogen trends and flow-effects of the San Joaquin river at C10, 
\item effects of wastewater treatment upgrades upstream of P8, and
\item effects of biological invasion on nutrient dynamics in Suisun Bay.
\end{inparaenum}
Each case study is built around hypotheses that results from \ac{wrtds} models were expected to support, both as a general description and for additional testing with alternative methods.

\subsubsection{Disaggregating observed nitrogen time series}

Multiple biological and physical factors influence nutrient concentrations at different temporal scales \cite{Cloern10}.  As a result, relationships between nutrients, time, and flow that could be described by quantitative methods like \ac{wrtds} are espected to be non-linear and complex as compared to more conventional methods for time series analysis.  A detailed evaluation of nitrogen dynamics at C10 using \ac{wrtds}, including the effects of flow, was expected to reveal \begin{inparaenum}[1\upshape)]
\item an annual trend independent of a seasonal trend, and 
\item varying flow contribution to nutrient dynamics, either as a difference between predicted and flow-normalized results or changes in the nutrient versus flow relationship at different annual periods.
\end{inparaenum}
Results from this case study were used to demonstrate the breadth of information that can be obtained from the observed time series with \ac{wrtds}.

@@

@@

\subsubsection{Disaggregating observed nitrogen time series}

\cref{fig:dinc10}, \cref{fig:dinc10dyna}

Emphasize the information the model provides relative to the observed time series.  A distinct annual trend with a maximum in the middle of the time series is observed, with lower values at the beginning and end of the period.  The seasonal patterns generally showed that \ac{din} concentrations were highest in January with higher values at moderate to low flow rates depending on the year. Interestingly, summer and fall concentrations have showed a slight increase later in the time series (~2004-2009).  The confounding effect of flow is also very apparent such that higher flows were associated with lower concentration.  Dynaplot showed that there was always a negative assocation between the two (i.e., no modal response).  The quantile distributions showed similar trends over time in both predicted values and flow-normalized predictions, although some exceptions were observed.  In particular, high flow (1984, 2008) reduced concentrations of all quantiles but the magniutude of the effect increased at higher quantiles (i.e., the effect was disproportionate).  The opposite was observed for low flow, i.e., the ninetieth percent showed the greatest increase for low flow.

Emphasize the summer/fall change in the 2000s, why is this?  Check \cite{Cloern07}, showed seasonal changes in early 2000s in chlorophyll (NE Pacific shifted to cool phase), is there a mechanism here with DIN? Relate to conceptual diagram.

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,page=1]{figs/delt_map.pdf}
\caption{The \acl{sfe} Delta and monitoring stations used for analysis. The Delta drains the combined watershed from the Sacramento and San Joaquin rivers (bottom left). All data were obtained from the \acl{iep} website (\url{http://water.ca.gov/bdma/meta/Discrete/data.cfm})\cite{IEP13}.}
\label{fig:delt_map}   
\end{figure}

@@

@@

<<dinc10, fig.height = 8, fig.width = 7, cache = T, out.width = '0.75\\textwidth', fig.cap = 'Time series of \\ac{din} and flow at station C10.  Subfigure (a) shows the observed \\ac{din} time series and subfigure (b) shows the annual (water year starting in October) predictions from \\ac{wrtds} at different conditional quantiles ($\\tau$ = 0.1, 0.5, 0.9).  The points in subfigure (b) are predictions of observed \\ac{din} and the lines are flow-normalized predictions.  Subfigure (c) shows the difference between the model predictions and flow-normalized predictions at the fiftieth conditional quantile.  Subfigure (d) shows the flow time series of the San Joaquin River with a locally-estimated (loess) smooth to emphasize the long-term trend.'>>=

# globals
ylab <- expression(paste('DIN (mg ', L^-1, ')'))
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    axis.title.x = element_blank(),
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm") 
  )
col_vec <- RColorBrewer::brewer.pal(9, 'Blues')[c(9, 8, 7)]
col_lim <- c(0, 3.8)
xlims <- range(toplo$date)
txt <- data.frame(
  x = max(toplo$date), 
  y =  c(5, 2.4, 0.5, 7), 
  txt = c('(a)', '(b)', '(c)', '(d)')
)
size <- 7

# observed din
toplo1 <- select(toplo, date, res) %>% 
  na.omit()
p1 <- ggplot(toplo1, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab) +
  theme(
    axis.text.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  geom_text(data = txt[1, ], aes(x = x, y = y, label = txt), size = size) +
  scale_x_date(limits = xlims)

# din prdnrmplot
p2 <- prdnrmplot(toplo, logspace = F, col_vec = col_vec) + 
  ptheme + 
  scale_y_continuous(ylab) +
  theme(
    legend.position = 'top', 
    axis.text.x = element_blank(),
    legend.title = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size) +
  scale_x_date(limits = xlims)

# flo/observed diffs
toplo2 <- prdnrmplot(toplo, plot = F)
toplo2 <- left_join(toplo2$fits, toplo2$nrms, by = c('date')) %>% 
  mutate(flodiff = fits_variable - nrms_variable)
toplo3 <- toplo
toplo3$flo <- scales::rescale(toplo3$flo, to = attr(toplo, 'floobs_rng'))
ylab <- expression(paste('Pred - norm DIN (mg ', L^-1, ')'))
p3 <- ggplot(toplo2, aes(x = date, y = flodiff)) + 
  geom_bar(stat = 'identity') + 
  theme_minimal() +
  ptheme + 
  theme(
    axis.text.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
    ) + 
  scale_y_continuous(ylab) +
  scale_x_date(limits = xlims) +
  geom_text(data = txt[3, ], aes(x = x, y = y, label = txt), size = size)

# flo with loess
ylab <- expression(paste('ln-Flow (', m^3, ' ', s^-1, ')'))
p4 <- ggplot(toplo3, aes(x = date, y = flo)) + 
  geom_line() +
  stat_smooth(se = F) + 
  ptheme + 
  scale_y_continuous(ylab) +
  scale_x_date(limits = range(toplo3$date)) +
  geom_text(data = txt[4, ], aes(x = x, y = y, label = txt), size = size)

# align widths of plots in first column, first two
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
pC <- ggplot_gtable(ggplot_build(p3))
pD <- ggplot_gtable(ggplot_build(p4))
maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3], pC$widths[2:3], pD$widths[2:3])

pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth
pD$widths[2:3] <- maxWidth

grid.arrange(
  pA, pB, pC, pD,
  heights = c(0.9, 1.3, 1, 1.2),
  ncol = 1
  )

<<dinc10dyna, fig.height = 6, fig.width = 9, cache = T, out.width = '\\textwidth', fig.cap = 'Modelled relationships between \\ac{din}, flow, and time at station C10.  The top figure shows the annual and seasonal variation over the entire time series and the bottom figure shows annual variation for selected months to remove seasonal variation.  Warmer colors indicate higher \\ac{din} concentrations.  The y-axis on the bottom figure is truncated by the fifth and ninety-fifth percentiles of flow within each month.  Model results are for the fiftieth conditional quantile of \\ac{din}.'>>=

# globals
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"),
    axis.title.x = element_blank()
  )
col_lim <- c(0, 3.8)
txt <- data.frame(
  x = min(toplo$date), 
  y =  c(5, 2.4, 0.5, 6), 
  txt = c('a', 'b', 'c', 'd')
)
size <- 7

# dynaplot, all
col_vec = NULL
attr(toplo, 'reslab') <- expression(paste("DIN (mg ", L^-1, ")"))
ylab <- expression(paste('ln-Flow (', m^3, ' ', s^-1, ')'))
p1 <- gridplot(toplo, month = 'all', logspace = F, col_lim = col_lim, floscl = F, col_vec = rev(col_vec)) +
  scale_y_continuous(ylab, expand = c(0, 0)) + 
  ptheme + 
  theme(legend.position = 'top')

# dynaplot selected months
p2 <- gridplot(toplo, logspace = F, col_lim = col_lim, month = c(1, 4, 7, 10), ncol = 4, floscl = F) + 
  ptheme + 
  theme(
    strip.background = element_blank(),
    legend.position = 'none', 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
    ) + 
  scale_y_continuous(ylab, expand = c(0, 0))

# align widths of plots in first column, first two
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3])

pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth

grid.arrange(
  pA, pB,
  heights = c(1.2, 1),
  ncol = 1
  )
@

@@

ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"),
    axis.title.x = element_blank()
  )
cols <- RColorBrewer::brewer.pal(9, 'Blues')[c(3, 5, 8)]

@@

p1 <- ggplot(toplo2) + 
  geom_area(aes(x = date, y = val, group = var, fill = var), stat = 'identity', position = 'stack') + 
  scale_x_date(expand = c(0, 0), limits = xrng) + 
  scale_fill_manual(values = cols, labels = leglabs) + 
  geom_vline(xintercept = as.numeric(lndate), linetype = 'dashed') +
  geom_label_repel(
    data = data.frame(x = lndate, y = 35), 
    aes(x, y, label = 'WWTP upgrades'), 
    box.padding = grid::unit(2, "lines"), 
    nudge_x = 1
    ) +
  scale_y_continuous(ylab1, expand = c(0, 0)) + 
  ptheme + 
  theme(
    legend.position = 'top', 
    legend.title = element_blank()
    )

>>>>

% \usepackage[version=3]{mhchem}
\usepackage[T1]{fontenc}
\usepackage[colorlinks  =true, allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{lineno}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage{paralist}
\usepackage{bm}
\usepackage{fixltx2e}
\usepackage{showlabels}

@@

The goal of this study was to provide a comprehensive description of nutrient trends in the Delta that will inform understanding of eutrophication dynamics and potential causes of water quality change in the larger Bay. We applied the newly-adapted method of weighted regression for tidal waters to describe nitrogen trends in  different spatial and temporal contexts. The specific objectives were to \begin{inparaenum}[1\upshape)]  
\item quantify and interpret trends over four decades at ten stations in the Delta, including annual, seasonal, and spatial changes in nitrogen analytes and response to flow variation,
\item provide detailed descriptions of two case studies in the context of conceptual relationships modelled with \ac{wrtds}.
\end{inparaenum}
The second objective evaluated two specific water quality stations in the Delta to demonstrate complexities with nutrient response to flow, effects of \ac{wwtp} upgrades on water quality, and effects of biological invasion by benthic filter feeders on primary production. Although quantitative descriptions of change can be ends in themselves, the results were expected to have greater impact as a means to more detailed understanding of ecosystem properties.  Products derived from \ac{wrtds} can be used to inform additional analyses, such as water quality response after removing annual, seasonal, or flow effects. Overall, this analysis is expected to further an ecological and management-based understanding of dynamics in San Francisco Bay, with implications for water quality restoration and protection of this prominent system.

@@

@@

kendall tests - observed

What about flow? \cref{fig:dinc10}, \cref{fig:dinc10dyna}

Emphasize the information the model provides relative to the observed time series.  A distinct annual trend with a maximum in the middle of the time series is observed, with lower values at the beginning and end of the period.  The seasonal patterns generally showed that \ac{din} concentrations were highest in January with higher values at moderate to low flow rates depending on the year. Interestingly, summer and fall concentrations have showed a slight increase later in the time series (~2004-2009).  The confounding effect of flow is also very apparent such that higher flows were associated with lower concentration.  Dynaplot showed that there was always a negative assocation between the two (i.e., no modal response).  Emphasize the summer/fall change in the 2000s, why is this?  Check \cite{Cloern07}, showed seasonal changes in early 2000s in chlorophyll (NE Pacific shifted to cool phase), is there a mechanism here with DIN? Relate to conceptual diagram.

@@

Two stations were chosen for closer evaluation to demonstrate use of \ac{wrtds} to develop a more comprehensive description of decadal trends in the Delta.  The stations were chosen to address ecological and management-based questions that have relevance outside of the region, having importance for the understanding of estuarine processes that influence eutrophication trends over several years.  The selected case studies focused on \begin{inparaenum}[1\upshape)]
\item effects of wastewater treatment upgrades upstream of P8, and
\item effects of biological invasion on nutrient dynamics in Suisun Bay.
\end{inparaenum}
Each case study is built around hypotheses that results from \ac{wrtds} models were expected to support, both as a general description and for additional testing with alternative methods.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth,page=1]{figs/delt_map.pdf}
\caption{The \acl{sfe} Delta and monitoring stations used for analysis. The Delta drains the combined watershed from the Sacramento and San Joaquin rivers (bottom left). All data were obtained from the \acl{iep} website (\url{http://water.ca.gov/bdma/meta/Discrete/data.cfm})\cite{IEP13}.}
\label{fig:delt_map}   
\end{figure}

@@

<<dinc10, fig.height = 9, fig.width = 7, cache = T, out.width = '0.75\\textwidth', fig.cap = 'Time series of \\ac{din} and flow at station C10.  Subfigure (a) shows the observed \\ac{din} time series and subfigure (b) shows the annual (water year starting in October) predictions from \\ac{wrtds} at different conditional quantiles ($\\tau$ = 0.1, 0.5, 0.9).  The points in subfigure (b) are predictions of observed \\ac{din} and the lines are flow-normalized predictions.  Subfigure (c) shows the difference between the model predictions and flow-normalized predictions at the fiftieth conditional quantile.  Subfigure (d) shows the flow time series of the San Joaquin River with a locally-estimated (loess) smooth to emphasize the long-term trend. Subfigure (e) shows the modelled relationships between \\ac{din}, flow, and time.'>>=

# globals
ylab <- expression(paste('DIN (mg ', L^-1, ')'))
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    axis.title.x = element_blank(),
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"), 
    legend.position = 'top',    
    legend.title = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  )
col_vec <- RColorBrewer::brewer.pal(9, 'Blues')[c(9, 8, 7)]
col_lim <- c(0, 3.8)
xlims <- range(toplo$date)
txt <- data.frame(
  x = max(toplo$date) - 300, 
  y =  c(5, 2.4, 0.6, 7, 7), 
  txt = c('(a)', '(b)', '(c)', '(d)', '(e)')
)
size <- 5

# observed din
toplo1 <- select(toplo, date, res) %>% 
  na.omit()
p1 <- ggplot(toplo1, aes(x = date, y = exp(res))) + 
  geom_line() + 
  scale_y_continuous(ylab) +
  geom_text(data = txt[1, ], aes(x = x, y = y, label = txt), size = size) +
  scale_x_date(limits = xlims, expand = c(0, 0)) +
  ptheme

# din prdnrmplot
p2 <- prdnrmplot(toplo, logspace = F, col_vec = col_vec) + 
  scale_y_continuous(ylab) +
  geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size) +
  scale_x_date(limits = xlims, expand = c(0, 0)) +
  ptheme

# flo/observed diffs
toplo2 <- prdnrmplot(toplo, plot = F)
toplo2 <- left_join(toplo2$fits, toplo2$nrms, by = c('date')) %>% 
  mutate(flodiff = fits_variable - nrms_variable)
toplo3 <- toplo
toplo3$flo <- scales::rescale(toplo3$flo, to = attr(toplo, 'floobs_rng'))
ylab <- expression(paste('Pred - norm DIN (mg ', L^-1, ')'))
p3 <- ggplot(toplo2, aes(x = date, y = flodiff)) + 
  geom_bar(stat = 'identity') + 
  scale_y_continuous(ylab) +
  scale_x_date(limits = xlims, expand = c(0, 0)) +
  geom_text(data = txt[3, ], aes(x = x, y = y, label = txt), size = size) +
  ptheme

# flo with loess
ylab <- expression(paste('ln-Flow (', m^3, ' ', s^-1, ')'))
p4 <- ggplot(toplo3, aes(x = date, y = flo)) + 
  geom_line() +
  stat_smooth(se = F) + 
  scale_y_continuous(ylab) +
  scale_x_date(limits = range(toplo3$date), expand = c(0, 0)) +
  geom_text(data = txt[4, ], aes(x = x, y = y, label = txt), size = size) +
  ptheme

# dynaplot, all
txte <- txt[5, , drop = FALSE]
txte[, 'x'] <- lubridate::decimal_date(txte[, 'x'])
txte$res <- 0
attr(toplo, 'reslab') <- expression(paste("DIN (mg ", L^-1, ")"))
ylab <- expression(paste('ln-Flow (', m^3, ' ', s^-1, ')'))
p5 <- gridplot(toplo, month = 'all', logspace = F, col_lim = col_lim, floscl = F) +
  scale_y_continuous(ylab, expand = c(0, 0)) +
  geom_text(data = txte, aes(x = x, y = y, label = txt), size = size) +
  theme(
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
    )

# align widths of plots in first column, first two
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
pC <- ggplot_gtable(ggplot_build(p3))
pD <- ggplot_gtable(ggplot_build(p4))
pE <- ggplot_gtable(ggplot_build(p5))
maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3], pC$widths[2:3], pD$widths[2:3], pE$widths[2:3])

pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth
pD$widths[2:3] <- maxWidth
pE$widths[2:3] <- maxWidth

grid.arrange(
  pA, pB, pC, pD, pE,
  heights = c(1, 1.3, 1, 1, 1.5),
  ncol = 1
  )

@@

@@

ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"),
    axis.title.x = element_blank(),
    legend.position = 'top', 
    legend.title = element_blank()
  )
cols <- RColorBrewer::brewer.pal(9, 'Blues')[c(3, 5, 8)]

@@

p1 <- ggplot(toplo2) + 
  geom_area(aes(x = date, y = val, group = var, fill = var), stat = 'identity', position = 'stack') + 
  scale_x_date(expand = c(0, 0), limits = xrng) + 
  scale_fill_manual(values = cols, labels = leglabs) + 
  geom_vline(xintercept = as.numeric(lndate), linetype = 'dashed') +
  geom_label_repel(
    data = data.frame(x = lndate, y = 35), 
    aes(x, y, label = 'WWTP upgrades'), 
    box.padding = grid::unit(2, "lines"), 
    nudge_x = 1
    ) +
  scale_y_continuous(ylab1, expand = c(0, 0)) + 
  ptheme

### 2017-01-09 sftrends_manu.tex
annual per chg removed from trndmap
dynaplot to fig dinc10

{\centering \includegraphics[width=0.8\textwidth]{figs/obsdat-1}

@@

\caption{Observed \ac{din} from ten stations in the upper \ac{sfe} Delta.  Data were collected monthly and evaluated with \ac{wrtds} models from 1976 to 2013. Note different y-axis scales.  See \cref{fig:delt_map} for station locations.}\label{fig:obsdat}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{figs/trndmap-1}

@@

\caption{Time series of \ac{din} and flow at station C10.  Subfigure (a) shows the observed \ac{din} time series and subfigure (b) shows the annual (water year starting in October) predictions from \ac{wrtds} at different conditional quantiles ($\tau$ = 0.1, 0.5, 0.9).  The points in subfigure (b) are predictions of observed \ac{din} and the lines are flow-normalized predictions.  Subfigure (c) shows the difference between the model predictions and flow-normalized predictions at the fiftieth conditional quantile.  Subfigure (d) shows the flow time series of the San Joaquin River with a locally-estimated (loess) smooth to emphasize the long-term trend.}\label{fig:dinc10}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{figs/dinc10dyna-1}

@@

\caption{Modelled relationships between \ac{din}, flow, and time at station C10.  The top figure shows the annual and seasonal variation over the entire time series and the bottom figure shows annual variation for selected months to remove seasonal variation.  Warmer colors indicate higher \ac{din} concentrations.  The y-axis on the bottom figure is truncated by the fifth and ninety-fifth percentiles of flow within each month.  Model results are for the fiftieth conditional quantile of \ac{din}.}\label{fig:dinc10dyna}
\end{figure}

>>>>

{\centering \includegraphics[width=0.9\textwidth]{figs/obsdat-1}

@@

\caption{Observed \ac{din} (NH$_4^{+}$ + NO$_2^{-}$/NO$_3^{2-}$) from ten stations in the upper \ac{sfe} Delta.  Data were collected monthly and evaluated with \ac{wrtds} models from 1976 to 2013. Note different y-axis scales.  See \cref{fig:delt_map} for station locations.}\label{fig:obsdat}
\end{figure}

@@

@@

\caption{Time series of \ac{din} and flow at station C10.  Subfigure (a) shows the observed \ac{din} time series and subfigure (b) shows the annual (water year starting in October) predictions from \ac{wrtds} at different conditional quantiles ($\tau$ = 0.1, 0.5, 0.9).  The points in subfigure (b) are predictions of observed \ac{din} and the lines are flow-normalized predictions.  Subfigure (c) shows the difference between the model predictions and flow-normalized predictions at the fiftieth conditional quantile.  Subfigure (d) shows the flow time series of the San Joaquin River with a locally-estimated (loess) smooth to emphasize the long-term trend. Subfigure (e) shows the modelled relationships between \ac{din}, flow, and time.}\label{fig:dinc10}
\end{figure}

@@

{\centering \includegraphics[width=0.7\textwidth]{figs/trndmap-1}

@@
